\documentclass[12pt]{article}
\usepackage{graphicx}
\usepackage{standalone}
\usepackage{import}
\usepackage{amsmath}
\usepackage{hyperref}
\usepackage{verbatim}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=cyan,
    pdfpagemode=FullScreen,
    }
\let\oldsection\section
\renewcommand\section{\clearpage\oldsection}
\title{
Boris Pusher Theory Booklet}
\author{Sidney Williams}
\newtheorem{theorem}{Theorem}
\newtheorem{corollary}{Corollary}
\newtheorem{proof}{Proof}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\begin{document}
\maketitle
\tableofcontents
\section{Introduction}

This booklet covers all the theory that I needed during my 2021 SULI when I was writing my Boris pusher code. This is by no means a replacement for any course, nor a statement of a completed project. Instead, I hope that this booklet allows anyone to "pick up and play" with the code that I have written this summer. I do say "I have written", I actually took the base code from this \href{https://www.youtube.com/watch?v=d4NlmGkfagk&t=889s&ab_channel=PyPhy}{video}, it was nothing close to what I needed for my project, so I changed its character completely, but the basic Boris mechanism that was originally in place is still there, so I need to cite where that came from. In the nature of modification though, I hope that this will be a living, breathing animal. I will be uploading the code and this theory booklet to Git with the intention of other people modifying both this booklet and the code to their purposes, all I ask is that unless some functionality is outright incorrect, that it is not taken out. As of now, I feel that what should be added is an extension to relativity, and particle-particle interactions, I am no means an expert on everything that this algorithm can do, but that felt like the logical next step as I was working. Happy coding!

-Sidney Williams August 2021 
\section{Electricity and Magnetism}\cite{Stacey}
\import{Individual/}{EMBasics}
\section{Plasma Physics}
\subsection{Gyro-Orbit}
\import{Individual/}{Gyro.Orbit}
\subsection{Drifts}\label{subsecdrifts}
\import{Individual/}{Drifts}
\subsection{Adiabatic Invariants}
\import{Individual/}{Adiabatic.Invariant}
\subsection{Magnetic Mirror}
\subsubsection{Rotating Magnetic Mirror}
\import{Individual/}{Rotating.Mirror}
\subsubsection{Worked Asymmetric Magnetic Mirror Problem}\label{subsecgenexam}
\import{Individual/}{Generals.Problem}
\section{Code and Numerical Theory}
\import{Individual/}{Numeric.Theory}

\bibliographystyle{plain}
\bibliography{./Individual/TB}
\end{document}